\documentclass[english]{article}
\usepackage[utf8]{inputenc}
\usepackage{babel,textcomp,csquotes,ifimasterforside,varioref,graphicx}
\usepackage[T1]{fontenc}
\usepackage[hyphens]{url} % deler lange url-er

% biblatex-pakka med opsjoner
\usepackage[backend=biber,%
%style=numeric,%
backref,%
sortcites,%
defernumbers=true,%
style=authoryear%
%style=alphabetic%
%sorting=none,% eller nty, nyt o.a
%date=long,% eller short, terse, comp, iso8601
]{biblatex}

% må opplyse om bib-filen
% ved flere bib-filer gjentas kommandoen
\addbibresource{bibliography.bib}

% denne kommandoen er for reftex som ikke forstår BibLaTeX
%\bibliography{referanser}

% noen mulige lokale biblatex tilpasninger
%\DefineBibliographyStrings{norsk}{%
%   urlseen={Sett: },
%   bibliography = {Bibliografi},
%   references = {Referanser},
%   editor = {redaktør},
%   translator={oversetter},
   %page={side},
   %pages={sidene},
%   and={og}
%}

\DeclareFieldFormat{url}{\url{#1}} % fjerner hardkodet "URL: " foran url

\DeclareUrlCommand\url{\def\UrlLeft{\newline}\def\UrlRight{\newline}%
\urlstyle{sf}} % setter inn passende linjeskift

% biblatex anbefaler at hyperref blir lastet inn etter biblatex
\usepackage{hyperref}

\title{}
% Sett inn ditt eget navn her:
\author{Johannes Akse}

\begin{document}
\maketitle{}
%Example of siting: their jobs, rather than the programmer's \parencite {shneiderman1983}\parencite{stephenson1999,hutchins1986},.
\tableofcontents
\nocite{*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

\subsection{Goal}

\subsection{Development in a real time setting}
Even though the functionality looks easy, the development has not been trivial. 

\subsection{Gsuite - A need to simplify the UI}

\subsection{Requirement specifications}

\subsection{Design choices}

\subsection{Challenges}

\subsection{Problem statement}

\subsection{Terminology}
\subsubsection{Acronyms}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Background %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Background}

\subsection{Web clients}

\subsection{Anticipated behavior in a web application}

\subsection{Single page application on top of server heavy page - A hack?}

\subsection{Storing state in the browser}

\subsection{Location.hash or models as driving appliBehaviourcation state}

\subsection{Communicating with the DOM}

\subsection{Strictly objects vs class structures} (Discussion?)
\subsubsection{ECMA 5 vs ECMA 6} (Discussion?)

\subsection{Using third party libraries or design from scratch?} (Discussion?)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Methodology %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methodology}
Why local testing has been crucial to development 

\subsection{Behavior driven development}
Find source.

\subsubsection{Jasmine}
Using Jasmine as integration testing tool

\subsection{Modularity}
For modularity and encapsulation. (Discussion?)
\subsubsection{Browserify, taking Nodejs NPM module loading technology to the browser}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Development %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Development}
\subsection{Building blocks / Objects}
\subsubsection{Main}
ModeApp
ToolApp
\subsubsection{Prototypes}
Model prototype
View prototype
Controller prototype
History prototype
Dispatcher prototype
Observer


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Discussion %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Discussion}
\subsection{Specific or broad approach}
* Code for the future ie pushState
* Both setHistory and changeHistory
c - More work. More mess
p - Faster refactoring when new specifications

* uriAnchor vs. own development
* How to handle bugs in third party plugins?
* Using framework or library vs creating from scratch (Introduced in the background).
* Local storage vs simple

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Conclusion %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion}

\subsection{Thoughts on future development}



\newpage
% The headline of the bibliography (the document class article)
\renewcommand{\refname}{Bibliography}

% redefiner \bibname ved bruk av dokumentklassen book

% Litteraturlista inn i innholdsfortegnelsen
\addcontentsline{toc}{section}{\refname}

\printbibheading
\printbibliography[type=book, title={Books}]
\printbibliography[type=article, title={Articles}]
\printbibliography[type=manual, title={Manuals}]
\printbibliography[nottype=book, nottype=article,%
nottype=manual, title={Other documents}]

\end{document}
